\documentclass[10pt]{article}
\usepackage[a4paper,margin=1.7cm,top=.5cm]{geometry}

% Language!
\usepackage[english]{babel}

% Font
\usepackage[default]{comicneue}
\usepackage[T1]{fontenc}

% Links
\usepackage[unicode=true]{hyperref}
\hypersetup{pdfborder={0 0 0},
            breaklinks=false}
% \urlstyle{same}  % don't use monospace font for urls

% Spacing
\frenchspacing
\newcommand{\setparskip}{\setlength{\parskip}{.3em}}
\setparskip
\setlength{\parindent}{0em}

% Misc

\date{}
\title{Tom Houlé}
\author{}

\pagenumbering{gobble}

\begin{document}

\maketitle

\vspace{-16mm}

\begin{center}
email: tom~[at]~tomhoule.com $\diamond$ github: \href{https://github.com/tomhoule}{@tomhoule} $\diamond$ blog: \url{https://tomhoule.com} $\diamond$ based in Berlin
\end{center}

\vspace{10mm}

\begin{minipage}[t]{0.54\textwidth}
  \setparskip

  \section*{Experience}

  \subsubsection*{since 2019 $\diamond$ Rust Engineer, Tech Lead at Prisma}

    \vspace{-0.8em}

    Since January 2023, engineer on the Client Team, responsible for the Query
    Engine behind Prisma Client.

    Previously Tech Lead of the Schema Team. The team is responsible for the Migrate
    and Introspection products, as well as the general space of database schema
    management and the Prisma Schema Language implementation and tooling.

    Designed and shipped the new Migrate product, and drove many smaller
    projects to completion (performance analysis, extended database type
    support, testing infrastructure, …). Frequent collaboration with external
    stakeholders (users, framework authors, database drivers). Significant
    amount of discovery and feature design work. Representing Prisma on the
    board of the GraphQL Foundation.

    Code samples: \\
    \url{https://github.com/prisma/prisma-engines/commits?author=tomhoule}

    \vspace{-0.5em}

    \subsubsection*{2016~--~2019 $\diamond$ Full Stack Developer, Senior Full Stack Developer, Tech Lead at store2be}

    \vspace{-0.8em}

    Second engineering hire in a Berlin B2B SaaS startup. Stack:~Rails, React,
    Postgres, Redis. Introduced and drove adoption of
    TypeScript, GraphQL. Strong collaboration practices: regular pair programming, systematic, thorough code reviews, regular 1:1s, TDD, product-oriented thinking.

    Took an active part in infrastructure work (notably, migration from Heroku
    to Kubernetes, Terraform).

    Tech Lead role for the Backend Team in the last year, with regular 1:1s with
    my reports, carreer planning and more formal feedback rounds.

    \vspace{-0.5em}

    \subsubsection*{2015~--~2016 $\diamond$ Full Stack Developer at Médiéval-AFDP (Lyon)}

    \vspace{-0.8em}

    Developed new web applications and enhanced older websites as the only
    full-time developer in a heritage-focused company working mostly for
    the public sector. Performed other tasks occasionally, such as web
    scraping and batch data manipulation. A few projects:
  %
    \begin{itemize}
    \item
      Cap Moderne: a relatively traditional website for an important cultural site
      on the French Riviera. Backend development, Django. $\rightarrow$ \url{https://capmoderne.com}
    \item
      Several web applications, including two used internally to manage public
      procurement offers and mailing lists. Django, Django REST Framework,
      React, Typescript.
    \item
      Safari de Peaugres: enhancement and modification of a legacy PHP website,
      with an new section written as an embedded React application.
    \end{itemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.42\textwidth}
  \setparskip

  2013 $\diamond$ Internship at the Fondation Alliance Française (Paris), working on a
  Foreign Affairs Ministry program for professional training in the French
  foreign cultural network.

  \section*{Technologies \& Interests}

  Long lived interest in \textbf{databases}, mostly from a practical point of
  view: how they are implemented, how they fit in a larger system.

  A large part of my current learning efforts are going into \textbf{formal
    methods}. Decent working grasp of proof assistants (Lean, Coq, Agda) and the
  underlying theory.  Not as knowledgeable, but interested in automatic
  verification. Using this as a learning vehicle for more maths and CS, a
  tremendous source of fun and maybe something to apply in the future.

  Long time \textbf{Rust} user who saw the language and ecosystem develop
  from the very early stages. You can find more and less recent samples of my
  code on GitHub.

  Familiar and comfortable with modern development and project management
  practices, more DevOps-related concerns like infrastructure management
  (Docker, k8s, also Ansible in the past), nix, the web plaftorm, \LaTeX...

  \section*{Education \& Languages}

  \paragraph{Degrees} Master's degree in Tourism and heritage studies, Lyon II university (2015), Master's degree in Political Science and projects management, Sciences Po Aix (2013)

  \vspace{-1em}

  \paragraph{Languages} French (native), English, German, Chinese (HSK level~6), Japanese (JLPT level~1), others as hobby.

  \vspace{-1em}

  \paragraph{Online course certificates} Functional programming principles in Scala (EPFL / Coursera), Functional programming design in Scala (EPFL / Coursera), Parallel programming (EPFL / Coursera)

\end{minipage}


\end{document}
